Calculating Entropies With Nested Sampling

### 2017-02-04 paper/ms.tex
impressive integration skillz

\renewcommand{\d}{\boldsymbol{d}}
\newcommand{\todo}{\color{orange} \bf}
\newcommand{\query}{\color{green} \bf}
\newcommand{\x}{\boldsymbol{\theta}}

@@

>>>>

\renewcommand{\d}{\boldsymbol{d}}
\newcommand{\todo}{\color{orange} \bf}
\newcommand{\query}{\color{green} \bf}
\newcommand{\x}{\boldsymbol{\theta}}
\newcommand{\n}{\boldsymbol{\eta}}

@@

The computational resources needed to compute these quantities are quite large,
though the algorithm can be parallelised trivially. However, the problem
being solved is not trivial. The mutual information of $\x$ and
$\d$ is
\begin{align}
I_{\x, \d} &= \int p(\x, \d) \log\frac{p(\x, \d)}{p(\x)p(\d)} \, d\x \, d\d.
\end{align}
However, $\x$ is one of several parameters. The others, $A$, and $\phi$,
were implicitly integrated out. Denoting the nuisance parameters by
$\n$, the mutual information that has been calculated is
\begin{align}
I_{\x, \d} &= \int p(\x, \d)
  \log\frac{\int p(\x, \n, \d) \, d\n }
           {p(\x) \int p(\x', \n)p(\d | \x', \n) \, d\x' \, d\n}
  \, d\x \, d\d.
\end{align}
It should not be considered surprising that this is a challenging task.
